Network Cascades

### 2016-08-26 paper/paper.tex
Add section foreshadowing bit

Section \ref{sec:model} presents a simple network cascade model as laid out by Watts\cite{simplemodel}.

In section \ref{sec:example}, a walk-through of a simulation of a simple graph is given.

@@

\section{Related Work}

@@

\section{Summary}\label{sec:summary}

>>>>

Section \ref{sec:model} presents a simple network cascade model as laid out by Watts\cite{simplemodel}. This is followed by a walk-through if a full simulation in section \ref{sec:example}.

In section \ref{sec:analysis}, the model is analyzed in regards to the possibility condition of global cascades. Section \ref{sec:findings} inspects the further results from Watts' research.

Section \ref{sec:threats} lists limitations and threats to validity of the original paper by Watts, which we discovered while compiling this work.

Finally, section \ref{sec:related-work} shows related work and section \ref{sec:summary} concludes the seminar paper's results.

@@

@@

\section{Related Work}\label{sec:related-work}

\section{Conclusion}\label{sec:summary}
